air4children: Artificial Intelligence and Robotics for Children

### 2021-03-07 slides/sources/air4children.tex
polished spiral learning fig [skip-all]

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
{
\paper{Elkin M., Sullivan A, Bers 2014 in Journal of Informantion and Technology}
\begin{frame}{AI and Robotics curriculum in Montessori Classroom}

  \it{The hand is the instrument of the mind.} Dr. Maria Montessori (1970-1952).
    \begin{figure}
        \centering
        \includegraphics[width=1.0\textwidth]{./figures/montessori/versions/drawing-v00.png}
        %\caption{}
      \end{figure}
\end{frame}
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
{
\paper{Mohammad T. et al., 2017; Harden R. M. and Stamper N in Journal of Medical Teacher}
\begin{frame}{Adopting Spiral Learning Methods in AIR4Children}

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
{
\paper{Elkin M., Sullivan A, Bers 2014 in Journal of Informantion and Technology}
\begin{frame}{Adopting Montessori Education in AIR4Children curriculum} 
  \vspace{3mm}
  \it{"The hand is the instrument of the mind."} Dr. Maria Montessori (1970-1952).
  \vspace{2mm}
    \begin{figure}
        \centering
        \includegraphics[width=1.0\textwidth]{./figures/montessori/versions/drawing-v00.png}
        %\caption{}
      \end{figure}
\end{frame}
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
{
\paper{Mohammad T. et al., 2017; Harden R. M. 1999 in Journal of Medical Teacher}
\begin{frame}{Adopting Spiral Learning Methods in AIR4Children curriculum}
